A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-17 papers/publication/paper-pollard.tex
conclusion

Moreover, the complexity of Graphalytics can obfuscate the true behavior of the program. By default, Graphalytics generates an HTML report listing the runtimes for each dataset and each algorithm in seconds. For example, one run of a single source shortest paths algorithm took 5.96 seconds. However, perusing the log files reveals a more complete picture: of these 5.96 seconds, 0.21 was spent computing the shortest paths while the remaining time consisted of building the necessary data structures. Furthermore, other performance-relavant details, such as the number of iterations run for PageRank, are not easily available using Graphalytics.
%We use GraphMat, the single source shortest paths algorithm, the dota-league dataset from the Game Trace Archive\cite{Guo:2012:GTA}, and the default settings as an example here.
% The full logs:
%Finished setting ids, time: 0.157009
%Starting sort
%Finished sort, time: 1.39571
%Finished setting edge pointers, time: 0.000133
%Starting build_dcsc
%Finished build_dcsc, time: 0.235948
%Finished setting ids, time: 0.154693
%Starting sort
%Finished sort, time: 1.75676
%Finished setting edge pointers, time: 0.000142
%Starting build_dcsc
%Finished build_dcsc, time: 0.238386
%Completed reading A from memory in 4.089144 seconds.
%Completed reading A from file in 5.114708 seconds
%Completed 19 iterations
%Timing results:
%- load graph: 5.11472 sec
%- initialize engine: 2.88486e-05 sec
%- run algorithm: 0.212451 sec
%- print output: 0.0799532 sec
%- deinitialize engine: 2.88486e-05 sec
%17:29:05.575 [INFO ] Benchmarking algorithm "Single source shortest paths" on graph "dota-league" took 5955 ms.

@@

We found Graphmat to not be highly performant but relatively scalable. One explanation is GraphMat's underlying computation model (sparse matrix operations) paired the increased overhead of GraphMat's doubly-compressed sparse row (DSCR) graph representation is more conducive to larger-scale graphs.
% Furthermore, sparse matrix operations have been well studied so achieving good scalability is more realistic [cite]

>>>>

Moreover, the complexity of Graphalytics can obfuscate the true behavior of the program. By default, Graphalytics generates an HTML report listing the runtimes for each dataset and each algorithm in seconds. For example, one run of a single source shortest paths algorithm took 5.96 seconds. However, perusing the log files reveals a more complete picture: of these 5.96 seconds, 0.21 was spent computing the shortest paths while the remaining time consisted of building the necessary data structures. Furthermore, other performance-relevant details, such as the number of iterations run for PageRank, are not easily available using Graphalytics.
%We use GraphMat, the single source shortest paths algorithm, the dota-league dataset from the Game Trace Archive\cite{Guo:2012:GTA}, and the default settings as an example here.
% The full logs:
%Finished setting ids, time: 0.157009
%Starting sort
%Finished sort, time: 1.39571
%Finished setting edge pointers, time: 0.000133
%Starting build_dcsc
%Finished build_dcsc, time: 0.235948
%Finished setting ids, time: 0.154693
%Starting sort
%Finished sort, time: 1.75676
%Finished setting edge pointers, time: 0.000142
%Starting build_dcsc
%Finished build_dcsc, time: 0.238386
%Completed reading A from memory in 4.089144 seconds.
%Completed reading A from file in 5.114708 seconds
%Completed 19 iterations
%Timing results:
%- load graph: 5.11472 sec
%- initialize engine: 2.88486e-05 sec
%- run algorithm: 0.212451 sec
%- print output: 0.0799532 sec
%- deinitialize engine: 2.88486e-05 sec
%17:29:05.575 [INFO ] Benchmarking algorithm "Single source shortest paths" on graph "dota-league" took 5955 ms.

@@

We found that GraphMat is not highly performant but does scale relatively well. One explanation is that GraphMat's underlying computation model (sparse matrix operations), paired the increased overhead of GraphMat's doubly-compressed sparse row (DSCR) graph representation, is better suited to larger-scale graphs.
% Furthermore, sparse matrix operations have been well studied so achieving good scalability is more realistic [cite]
